Cybersecurity Education Is Too Important\\To Be Left To The Specialists

### 2019-06-20 FIE2019-final-TPJHD.tex
A bit more shortening

Cybersecurity has increasingly been in the news over recent years, generally prompted by spectacular breaches of one kind or another, such as \cite{BritishAirways2018a}.
It needs attention across the spectrum:
\begin{quote}
change the culture in your organisation around cyber security; to try to do for cyber what has been done so successfully for health and safety, for example, over the last ten years --- to get everybody to take it seriously; to take the risk management process seriously and drive that down through the organisation. \cite{Hannigan2019a}\footnote{Former Director of GCHQ: British equivalent of NSA.}
\end{quote}

With this significant economic and societal focus on cybersecurity, there are calls for formal education -- school-level as well as post-compulsory -- to respond to this situation, which it does both at the individual level and via recommended curricula \cite{ACM2013a} and professional accreditation requirements \cite{BCS2018a}; this is alongside a wider focus on computer science education reform, especially across the UK~\cite{%crick+sentance:2011,brown-et-al:sigcse2013,
brown-et-al:toce2014,%wgictreview:2013,moller+crick:jce2018,davenport-et-al:latice2016,
murphy-et-al:programming2017%,simon-et-al:sigcse2018,tryfonas+crick:petra2018
}. There has been a recent Association for Computing Machinery (ACM)  working group as part of the Conference on Innovation and Technology in Computer Science Education \cite{Parrishetal2018a}, but this has yet to report.  The intention of this working group is to develop a taxonomy for approaches to cybersecurity education. The third aim of this working group is to ``catalog existing [\dots] knowledge materials'', but there is no mention of any quality control over these.

>>>>

Cybersecurity has increasingly been in the news over recent years, generally prompted by spectacular breaches, such as \cite{BritishAirways2018a}.
It needs attention across the spectrum \cite{Hannigan2019a}\footnote{Former Director of GCHQ: British equivalent of NSA.}:
\begin{quote}
change the culture in your organisation around cyber security; to try to do for cyber what has been done so successfully for health and safety, for example, over the last ten years --- to get everybody to take it seriously; to take the risk management process seriously and drive that down through the organisation. 
\end{quote}
\noindent
With this significant economic and societal focus on cybersecurity, there are calls for formal education -- school-level as well as post-compulsory -- to respond to this situation, which it does both at the individual level and via recommended curricula \cite{ACM2013a} and professional accreditation requirements \cite{BCS2018a}; this is alongside a wider focus on computer science education reform, especially across the UK~\cite{%crick+sentance:2011,brown-et-al:sigcse2013,
brown-et-al:toce2014,%wgictreview:2013,moller+crick:jce2018,davenport-et-al:latice2016,
murphy-et-al:programming2017%,simon-et-al:sigcse2018,tryfonas+crick:petra2018
}. There has been a recent Association for Computing Machinery (ACM)  working group as part of the Conference on Innovation and Technology in Computer Science Education \cite{Parrishetal2018a}, but this has yet to report.  The intention of this working group is to develop a taxonomy for approaches to cybersecurity education. The third aim of this working group is to ``catalog existing [\dots] knowledge materials'', but there is no mention of any quality control over these.
